---
title: "Plots for Midcourse Project"
output: html_document
date: "2023-01-07"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Add required Libraries
```{r}
library(dplyr)
library(tidyr)
library(readr)
library(ggplot2)
library(grid)
```

#read in Rdata File "prices"
```{r}
prices <- readRDS("prices.RData")
```

#ggplot dynamic histogram of distribution of List Price frequencies within given Format, Category, and Page Count filters -- annotations dynamic within given xlim params
```{r}
format <- 'Hardcover'
category <- 'JUVENILE FICTION'
pcb <- '51 - 100'
bins <- 30


p <- prices %>% 
  filter(Format == format & 
           BISAC_Level_1 == category & 
           page_count_bucket == pcb)

median <- median(p$List_Price_Value, na.rm = TRUE) %>% 
  format(round(2), nsmall = 2)

price_plot <- p %>% 
    ggplot(aes(x = List_Price_Value)) + 
    geom_histogram(color = 1, fill = 'skyblue', bins = bins) + 
    geom_vline(xintercept = median(p$List_Price_Value, na.rm = TRUE), 
             linetype="dotted", 
             color = 'red',
             lwd = 1) +
    coord_cartesian(expand = TRUE, clip = 'off') +
    scale_x_continuous(breaks = seq(0,1000, by = 10))

xlim <- layer_scales(price_plot)$x$range$range
ylim <- layer_scales(price_plot)$y$range$range

price_plot + 
  annotate("text",
             x = xlim[2] /2 + 2,
             y = ylim[2] /2 + 5,
             label = paste("Median (---) = $", median),
             color = "red",
             size = 4) +
      labs(x = 'List Price ($)', y = 'Frequency') +
      labs(title = "2022 List Price Frequency Distribution") +
      labs(caption = "Data: limited to 2022 pub dates w/ >= 3 reported sales (Ingram Book Company)")
```

#Bar Plot to visualize share of Level 2 categorization within Level 1 by frequency
```{r}
p2 <- prices %>% 
  filter(Format == format & BISAC_Level_1 == category) %>%
    group_by(BISAC_Level_1, BISAC_Level_2) %>% 
    summarize(count = n()) %>%
    arrange(desc(count))
  
p3 <- p2[1:10, ] %>% 
  mutate(relative_frequency = count/sum(count))
  
p3 %>%   
  ggplot(aes(x = BISAC_Level_2, y = relative_frequency, fill = 'skyblue')) +
  geom_bar(stat = "identity") +
  labs(x = "Category", y = "Top 10 Frequency") +
  labs(title = "Frequency of Top 10 Subcategories by Title Count") +
  labs(caption = "Data: limited to 2022 pub dates w/ >= 3 reported sales (Ingram Book Company)") +
  labs(legend.position = 'none') +
  guides(x = guide_axis(angle = -45))
```


#Horizontal Bar Plot to Show Top 20 Categories by Sales per Title metric
```{r}
p4 <- prices %>% 
        filter(Format == format & BISAC_Level_1 == category) %>%
        group_by(BISAC_Level_2) %>% 
        transmute(sales_per_title = Sales_2022/n_distinct(ISBN)) %>%
        arrange(desc(sales_per_title)) %>% 
        filter(duplicated(BISAC_Level_2) == FALSE)

p5 <- p4[1:20, ]

p5 %>% 
  ggplot(aes(x = sales_per_title, 
             y = reorder(BISAC_Level_2, sales_per_title), fill = 'skyblue')) +
  geom_col() +
  labs(x = "Sales per Title", y = "Category") +
  labs(title = "Top 20 Subcategories -- Sales per Title") +
  labs(caption = "Data: limited to 2022 pub dates w/ >= 3 reported sales (Ingram Book Company)") +
  theme(legend.position='none')
```

